Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-06 paper/content/inverted_u.tex
update eq strategies

\asedit{We assume that both firms play their respective equilibrium strategies for the corresponding competition level. As discussed previously, these are:}
\ascomment{Guy, pls fill in, and refer to the corresponding findings.}

>>>>

\asedit{We assume that both firms play their respective equilibrium strategies for the corresponding competition level} \gaedit{for $T_0 = 20$. As discussed previously, these are: (1) \DG in the monopoly, (2) \DG for both firms in duopoly from Finding \ref{find:duopoly}, (3) \TS for the incumbent (Finding \ref{find:temp-monopoly}) and \DG for the entrant in temporary monopoly (Finding \ref{find:temp-monopoly-entrant}).}
